---
title: "Variable Combination"
author: "Erin M. Buchanan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(rio)
```

## Data

```{r}
DF <- import("Melted Data Thesis.csv")
DF2 <- import("Melted Data pilot.csv")

colnames(DF2) <- colnames(DF)
totalDF <- rbind(DF, DF2)
```

## Check Data

```{r}
huge_test <- list()

for (wordpair in unique(totalDF$`Word Pair`)){
  temp <- totalDF[totalDF$`Word Pair` == wordpair , ]
  
  huge_test[[wordpair]] <- describe(temp)
  
}

hugeDF <- do.call(rbind, huge_test)
hugeDF$words <- rownames(hugeDF)

checkDF <- subset(hugeDF, sd != 0)
checkDF <- subset(checkDF, !grepl(".Partno|.Judg|.Recall", checkDF$words))
```

## Variables

Factors:

  - Overlap statistics: COS + LSA + FSG
  - Frequency: LogSub.1 + LogSub.2 + LogHAL.1 + LogHAL.2
  - Characteristics: Length.1 + Length.2 +  Phonemes.1 + Phonemes.2 + Syllables.1 + Syllables.2 + Morphemes.1 + Morphemes.2
  - Neighborhood: Ortho.1 + Ortho.2 + Phono.1 + Phono.2
  - Rated: AOA.1 + AOA.2 + Familiarity.1 + Familiarity.2 + Valence.1 + Valence.2 + Imageability.1 + Imageabilty.2 + QCON.1 + QCON.2 
  - Network: QSS.1 + TSS.2 + FSS.1 + FSS.2 + COSC.1 + COSC.2

